Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure 1

nldr1 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("a")

@@

# umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_12_min_dist_0.99.rds")
umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_5_min_dist_0.8.rds")
nldr2 <- umap_pbmc |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("b", c(0.08, 0.9))

@@

nldr3 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("c")

@@

nldr4 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("d")

@@

nldr5 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("e")

@@

phate_pbmc <- read_rds("data/pbmc3k/pbmc_phate_5.rds")
nldr6 <- phate_pbmc |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("f")

@@

trimap_pbmc <- read_rds("data/pbmc3k/pbmc_trimap_12_4_3.rds")
nldr7 <- trimap_pbmc |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("g")

@@

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.9_5.rds")
nldr8 <- pacmap_pbmc |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("h")

>>>>

nldr1 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("a", cex = 1.3)

@@

# umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_12_min_dist_0.99.rds")
umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_5_min_dist_0.8.rds")
nldr2 <- umap_pbmc |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("b", c(0.08, 0.9), cex = 1.3)

@@

nldr3 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("c", cex = 1.3)

@@

nldr4 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("d", cex = 1.3)

@@

nldr5 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("e", cex = 1.3)

@@

phate_pbmc <- read_rds("data/pbmc3k/pbmc_phate_5.rds")
nldr6 <- phate_pbmc |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("f", cex = 1.3)

@@

trimap_pbmc <- read_rds("data/pbmc3k/pbmc_trimap_12_4_3.rds")
nldr7 <- trimap_pbmc |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("g", cex = 1.3)

@@

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.9_5.rds")
nldr8 <- pacmap_pbmc |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("h", cex = 1.3)
